Enabling GPU Virtualization in Cloud Environments

### 2015-10-23 paper.tex
seccion 5 hasta 5.3 revisado

The second application, LAMMPS\footnote{\url{http://lammps.sandia.gov}}, 
is a classical molecular dynamics simulator that can be applied at the atomic, 
meso, or continuum scale. 
From the implementation perspective, this multi-process application employs 
at least one GPU to host its processes, but can benefit from the presence of multiple GPUs.
Figure~\ref{subfig:lammps1} shows that, for this application, the use of remote GPUs 
does not offer any advantage over the original CUDA. 
Furthermore, for the execution on remote GPUs, the difference between both networks is small, although, the ``High'' network performs worse than ``10 Gb'' network.
For execution of LAMMPS with a larger problem (see Figure~\ref{subfig:lammps2}), CUDA still performs better, but the interesting point is the execution time on remote GPUs. 
They are almost the same even with different networks which indicates that the transfers turn the interconnection network into a bottleneck, and enlarging the problem size
pays off the drawback of a slower network.

>>>>

The second application, LAMMPS\footnote{\url{http://lammps.sandia.gov}}, 
is a classical molecular dynamics simulator that can be applied at the atomic, 
meso, or continuum scale. 
From the implementation perspective, this multi-process application employs 
at least one GPU to host its processes, but can benefit from the presence of multiple GPUs.
Figure~\ref{subfig:lammps1} shows that, for this application, the use of remote GPUs 
does not offer any advantage over the original CUDA. 
Furthermore, for the execution on remote GPUs, the difference between both networks is small, although, the ``High'' network performs worse than ``10 Gb'' network.
For execution of LAMMPS with a larger problem (see Figure~\ref{subfig:lammps2}), CUDA still performs better, but the interesting point is the execution time on remote GPUs. 
They are almost the same even with different networks which indicates that the transfers turn the interconnection network into a bottleneck. For this type of application's 
patter, enlarging the problem size pays off the drawback of a slower network.
